Results: Describing the scale and composition of calls for police service: a replication and extension using open data

### 2025-03-18 results_summary.Rmd
repro run

---
title: 'Results: Describing the scale and composition of calls for police service: a replication and extension using open data'
author: Samuel Langton, Stijn Ruiter, Tim Verlaan
bibliography: refs.bib
output:
  pdf_document: 
    number_sections: true
header-includes:
  - \usepackage{lscape}
  - \usepackage{lineno}
csl: apa.csl
---

>>>>

---
title: 'Results: Describing the scale and composition of calls for police service: a replication and extension using open data'
author: Samuel Langton, Stijn Ruiter, Tim Verlaan
output:
  pdf_document: 
    number_sections: true
header-includes:
  - \usepackage{lscape}
  - \usepackage{lineno}
---
